Proof No Diamond (3 layers)

### 2025-12-12 CAV2026B_cart_pole/CAV2026_a_proof.tex
update

Consider $R = B_{\delta/4}(R_{\delta/2})$.
We show that $R$ satisfies:
$R_{\delta_2} \subsetneq R \subsetneq R_\delta$ 
with:
\begin{itemize}
	\item $I \subseteq R$,
	\item $B_{\delta/4}(R)\cup U = \emptyset$,
	meaning that $R$ is away from $U$,
	\item For all polytope $P$ on which 
    $\sigma$ is Liptscitz continuous (say with function $f$),
	for all $x \in P \cup R_{\delta/2}$ and 
	$y$ with $||y-x||<\delta/4$, 
	$succ(y,f(y)) \in R_{\delta/2}$.
\end{itemize}

@@

@@

\begin{lemma}
	There is a region $A$ satisfying the following:
	\begin{itemize}
			\item A is a union of polytopes.
		\item $A\supseteq R_{\delta/2}(I)$
		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
	\end{itemize}
	Hence, from $A$ we can construct a DT certificate.
\end{lemma}

%\begin{lemma}
%	Let $S$ be a system with policy $p$ and initial region $I$. For any $x\in R_r(I)$ and any $\varepsilon$, we have
%	\[
%	B_\varepsilon(x) \subseteq R_{r+\varepsilon }(I).
%	\]
%	Hence $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$.
%\end{lemma}
%
%\begin{proof}
%	To prove this lemma, fix $x \in R_r(I)$.
%	
%	We assume $x = x_{n+1}$ and $x_{n+1} = p(x_n)+d_n$ with $|d_n|<r$ and $x_n\in R_r(I)\cup I\subseteq R_{r+\varepsilon}(I)\cup I$. Then, we have \[
%	B_{\varepsilon}(x) \subseteq B_{|d_n| + \varepsilon}(p(x_n)) \subseteq B_{r + \varepsilon}(p(x_n)).
%	\]
%	
%	By definition, since $x_n\in R_{r+\varepsilon}(I)\cup I$, $B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I)$.
%	So,
%	\[
%B_{\varepsilon}(x) \subseteq
%	B_{r + \varepsilon}(p(x_n))\subseteq R_{r+\varepsilon}(I).
%	\]
%	This completes the proof.
%\end{proof}
%
%\vspace*{2ex}
%
%Notice that if $B_\varepsilon(R_r(I)) \subseteq R_{r+\varepsilon}(I)$, then $\operatorname{cl}(R_r(I)) \subseteq \operatorname{int}(R_{r+\varepsilon}(I))$. 
%
%\begin{proof}[of Theorem 1]
%	
%	We assume that $S$ is $\delta$-robustly safe.
%	
%	From Lemma 1, we can see that \begin{itemize}
%		\item $\operatorname{cl}(R(I)) \subseteq \operatorname{int}(R_\delta(I))$.
%		
%		\item Every point in $R(I)$ is at least a distance $\delta$ away from the boundary of $R_\delta(I)$.
%	\end{itemize}   
%	
%	
%	Therefore, we can partition the space into hypercubes of side length $\frac{\delta}{2\sqrt{n}}$ where $n$ is the dimension, and cover $R(I)$ with these hypercubes. Those hypercubes are in $R_\delta(I)$, and even $R_{\delta/2}(I)$.
%	
%	Put them together, we can get the following conclusion:
%	\begin{itemize}
%		\item There is a union of polytopes $\bigcup_{P \in \mathcal{P}} P$ contained in   $R_{\delta}(I)$ that covers $R(I)$.
%
%		\item Any point start from $\bigcup_{P \in \mathcal{P}} P$ following $S$ without perturbation will never enter $U$, and has a minimal distance from $U$.
%	\end{itemize}
%\end{proof}

>>>>

Consider $R = B_{\delta/4}(R_{\delta/2})$.
We show that $R$ satisfies:
$R_{\delta_2} \subsetneq R \subsetneq R_\delta$ 
with:
\begin{itemize}
	\item $I \subseteq R$,
	\item $B_{\delta/4}(R)\cup U = \emptyset$,
	meaning that $R$ is away from $U$,
	\item For all polytope $P$ on which 
    $\sigma$ is Liptscitz continuous (say with function $f$),
	for all $x \in P \cup R_{\delta/2}$ and 
	$y$ with $||y-x||<\delta/4$, 
	$succ(y,f(y)) \subseteq R_{\delta/2}$.
\end{itemize}

@@

To prove the third claim, we need to use the definition that $succ$ is also Lipschitz.

@@

%\begin{lemma}
%	There is a region $A$ satisfying the following:
%	\begin{itemize}
%			\item A is a union of polytopes.
%		\item $A\supseteq R_{\delta/2}(I)$
%		\item $A\subseteq\bigcup_{i\in I}B_\varepsilon(R_{\delta/2}(I)\cap Q_i)\cap Q_i$
%	\end{itemize}
%	Hence, from $A$ we can construct a DT certificate.
%\end{lemma}
